Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-20 paper-1/manuscript.tex
Rev sec Results:STD, F8 (done!)

To sum up, in the full model, STD acted in much the same way as TA, causing both a reduction of the response to the frequently presented standard stimuli (dev B) by adaptation, and an increase in the response to deviant stimuli (dev A) by relief from adaptation, relative to control. % ...

However, we also found that $D^A$ was greater in msc than dev (t = -3.4, p = 0.000458), suggesting that STD did exert stimulus-independent suppression in the msc sequence, similar to what we described earlier for TA. The magnitude of the effect, however, was very different. In the right half of Figure \ref{fig8}b, we show the contrast of $V_{TA}$ before A trials, which was clearly much greater than the contrast in $D^A$. We wondered, however, how much $V_{TA}$ was affected by the addition of STD. To assess this, we subtracted the contrast (dev - msc) of $V_{TA}$ in the full model from the same contrast calculated in the ablated model with TA only. This additional decrease in $V_{TA}$ from msc to dev was substantially greater than the corresponding decrease in $D^A$ (t = -1.93, p = 0.0277), indicating that the direct effect of STD on the target dev response was less than indirect effects.

To sum up, adding STD to the model had a number of direct and indirect effects. Firstly, it reduced responses in all conditions, likely by reducing the synaptic output of neurons at stimulus sites, which reliably fired several spikes immediately following stimulation. Secondly, it directly reduced the response to frequently presented dev B trials through stimulus-specific adaptation. Thirdly, STD was very slightly reduced in A trials in dev over msc, mirroring the direct stimulus-independent adaptation effect detailed in the previous section for TA. And finally, the decreased dev B trial response allowed TA in the wider network to recover more, which in turn led to increased responses in dev A trials. This indirect effect was substantially greater than the direct effect on target trials, as shown above, indicating that it was solely or largely responsible for the increased DDI.

>>>>

To sum up, in the full model, STD acted in much the same way as TA, causing both a reduction of the response to the frequently presented standard stimuli (dev B) by adaptation, and an increase in the response to deviant stimuli (dev A) by relief from adaptation, relative to control. Yet, as we showed in Figure \ref{fig7} and in the previous section, a decrease in dev B responses also entailed lower $V_{TA}$, and higher dev A response by consequence. Thus, adding STD to the model increased the DDI both directly, as outlined at the start of this paragraph, and indirectly, by altering the pattern of TA by way of changed responses.
